---
title: "Bin_Package_Problem"
author: "Ettore Falde"
date: "12/23/2021"
output: html_document
---

# Introduction 
The bin packing problem is an optimization problem, in which items of different sizes must be packed into a finite number of bins or containers, each of a fixed given capacity, in a way that minimizes the number of bins used. The problem has many applications, such as filling up containers, loading trucks with weight capacity constraints, creating file backups in media and technology mapping in FPGA semiconductor chip design.

Hence, in this assignemtn I develop two different solutions. 

1. he first solution is done by _MathProg_ and entirely done in R Studio. 

2. While the second solution is done in _Python_ due to efficiencies and a general better solution. 


# Set up
In order to complete the assignent we need those two packes that will permit our solution with MathProg
```{r}
# Libraries
library(Rglpk) 
library(slam)
```

# Solutions
As told before I develop two solutions: 

1. R Studio solution 

2. Python solution 

## R solution
### MathProg
First of all, I pass from the theory to the develop of the model in MathProg. This part could be done on a simple .txt editor or directly here in R Studio. 
```{r}
bins_problem <- '

/* The bin packing problem is aimed to pack I = {1,...,m}
elements of different volumes v[i] into bins each with a fixed capacity V
in a way that minimizes the number of bins used. */

  param m, integer, > 0;   /* number of elements to pack */
  set I := 1..m;           /* set of elements */
  param v{i in 1..m}, > 0; /* v[i] is volume of element i */
  param V, > 0;            /* bin capacity */

  /* worse scenario for the number of bins used */
  param n := m;


/* set of bins */
set J := 1..n;


/* x[i,j] = 1 means elemnt i is in bin j */
var x{i in I, j in J}, binary;


/* y[j] = 1 bin j is used */
var y{j in J}, binary;



/* each element of the set of elements must be contained in exactly one bin */
s.t. one{i in I}: sum{j in J} x[i,j] = 1;


/* the content of the bin must not exceed its capacity */
s.t. lim{j in J}: sum{i in I} v[i] * x[i,j] <= V * y[j];

/* the minimization of the number of bins used is the objective function of this problem */
minimize obj: sum{j in J} y[j];

  data;

param m := 10;

param v := 1 0.61, 2 0.96, 3 0.95, 4 0.91, 5 0.13, 6 0.53, 7 0.53, 8 0.05, 9 0.65, 10 0.66;

param V := 1;

end;

'
```


## Solve Function
Once, the model is designed, I was able to proceed input the _solve_lp_ function that can be called in order to obrain our output solution. 
```{r}
solve_lp <- function(model, type = "MathProg"){

  writeLines(model, "model.mod")

  lp_model <- Rglpk_read_file("model.mod", type = type)

  lp_solution <- Rglpk_solve_LP(obj = lp_model$objective,
                                mat = lp_model$constraints[[1]],
                                dir = lp_model$constraints[[2]],
                                rhs = lp_model$constraints[[3]],
                                types = lp_model$types,
                                bounds = lp_model$bounds,
                                max = lp_model$maximum)
  unlink("model.mod")

  if(lp_solution$status == 0){
    sol <- lp_solution$solution
    names(sol) <- attr(lp_model, "objective_vars_names")
    obj = lp_solution$optimum
    return(list(sol = sol, obj = obj, success = TRUE))
  }else
    return(success = FALSE)

}
```

### MathProg solve linear programming
In conclusion, I simply called the function wrote above and insert my model and specify the type = "MathProg" 
```{r}
solve_lp( bins_problem, type = "MathProg")
```

To conclude we can see a large output where: 

*_x[i,j]_ *--> represent the package i located in the container j
Therefore, when we see the number 1, that mean that one package is allocated in taht container. 

While for the output: *_y[j]_* --> that indicates is the bin was used or not (also here we have a boolean output 0 or 1)


## Python Solution
After having found the solution with MathProg, I noticed the extremely inefficiency that that solution has. 
Hence, in a separate file I coded the same solution as before in Python and thanks the package _ortools_ I was able to output a solution in extremely less time than before. 

In addition, this solution is more clear also for someone who want to understan what package locate and in where bin. 
```{r}
library(reticulate)

Sys.setenv(RETICULATE_PYTHON = "python/bin/python")

py_run_file("BPP.py")

```

```{python}
exec(open("BPP.py").read())
```





